Individual heterogeneity in the functional network topography of medial prefrontal cortex

### 2019-05-24 Manuscript.Rmd
and more small mistakes

We found a generalizable pattern across individual partitionings, in which the DN community covered ventral/dorsal mPFC and posterior PCC, with the non-DN community concentrated in pregenual ACC and anterior PCC. The precise spatial positioning of this general community structure was highly heterogenous across individuals, yet stable across test/re-test evaluations within-individual. The idiosyncrasy in functional topography was particularly pronounced in mPFC, and was identified in both run-based and day-based analyses. Individual-specificity could theoretically arise from a variety of sources. For example, the functional topography of mPFC could be governed by its underlying sulcal and gyral organization, which has been shown to vary systematically across individuals [@Mackey2014; Lopez2019]. Individual variability could also be due to shifts in functional organization that are independent of structural features [@Haxby2013], or be characterized by the pattern of functional connections with the rest of the brain [@Mars2018; @Passingham2002; @Tobyne2018]. An important goal for future work will be to assess whether the network layout in this region can be predicted on the basis of aspects of brain structure, such as sulcal morphology, myeloarchitecture [@Glasser2016], or structural connectivity [Osher2016; @Saygin2011; @Saygin2016].

>>>>

We found a generalizable pattern across individual partitionings, in which the DN community covered ventral/dorsal mPFC and posterior PCC, with the non-DN community concentrated in pregenual ACC and anterior PCC. The precise spatial positioning of this general community structure was highly heterogenous across individuals, yet stable across test/re-test evaluations within-individual. The idiosyncrasy in functional topography was particularly pronounced in mPFC, and was identified in both run-based and day-based analyses. Individual-specificity could theoretically arise from a variety of sources. For example, the functional topography of mPFC could be governed by its underlying sulcal and gyral organization, which has been shown to vary systematically across individuals [@Mackey2014; @Lopez2019]. Individual variability could also be due to shifts in functional organization that are independent of structural features [@Haxby2013], or be characterized by the pattern of functional connections with the rest of the brain [@Mars2018; @Passingham2002; @Tobyne2018]. An important goal for future work will be to assess whether the network layout in this region can be predicted on the basis of aspects of brain structure, such as sulcal morphology, myeloarchitecture [@Glasser2016], or structural connectivity [@Osher2016; @Saygin2011; @Saygin2016].
